A Partitioning Algorithm for Maximum Common Subgraph Problems

### 2017-02-17 paper/paper.tex
Change number to instances where we're fastest to percentage

\paragraph{Unlabelled, undirected}
\cref{figure:plain-cumulative} shows a plot of cumulative run times
against number of problem instances solved.  We may compare
the speed of two algorithms using the horizontal distance between their curves.
For example, we could solve 2,000 of the 4,110 unlabelled undirected instances
using the \McSplit\ algorithm if a time limit of 0.5 seconds per instance were
imposed.  Its nearest competitor, CP-FC, would require a time limit of over 24
seconds per instance to solve the same number of instances.  For any given
number of instances, \McSplit\ is comfortably more than an order of magnitude
faster than its nearer competitor  Moreover, there are few instances in this
set for which \McSplit\ is not the fastest solver; of the 3,506 instances that
could be solved by at least one of \McSplit, $k{\downarrow}$, CP-FC and clique in less than than
1,000 seconds, there were 426 instances on which \McSplit\ was not strictly
faster than the other two solvers.

>>>>

\paragraph{Unlabelled, undirected}
\cref{figure:plain-cumulative} shows a plot of cumulative run times
against number of problem instances solved.  We may compare
the speed of two algorithms using the horizontal distance between their curves.
For example, we could solve 2,000 of the 4,110 unlabelled undirected instances
using the \McSplit\ algorithm if a time limit of 0.5 seconds per instance were
imposed.  Its nearest competitor, CP-FC, would require a time limit of over 24
seconds per instance to solve the same number of instances.  For any given
number of instances, \McSplit\ is comfortably more than an order of magnitude
faster than its nearer competitor.  Moreover, \McSplit\ was the fastest algorithm
on 87\% of the 3,506 instances that
could be solved by at least one of the four algorithm in less than than
1,000 seconds.
